\documentclass{wlscirep}

\addbibresource{Library.bib}

\title{Dissecting Fc\textgamma{}R Regulation Through a Multivalent Binding Model}

\author[1]{Ryan A. Robinett}
\author[1,*]{Aaron S. Meyer}
\affil[1]{Koch Institute for Integrative Cancer Research, Massachusetts Institute of Technology, Cambridge, MA 02139}

\affil[*]{a@ameyer.me}

\keywords{Immune complex, multivalent ligand, receptor cross-linking, avidity, immunoglobulin G, Fc\textgamma{} receptors}

\begin{abstract}
Many immune receptors are transduce activation across the plasma membrane through their clustering. This clustering is usually achieved by binding to multivalent antigen. Models describing the binding of multivalent ligand presenting a single repeated epitope to monovalent receptors presenting a single paratope have been used to describe the binding of immune complexes to the surfaces of immune cells. One such model predicts that immune complexes can be designed such that, for any pair of receptors which bind to the aforementioned epitope with affinities of significantly different orders of magnitude, the number of receptors of the first kind that are clustered will be far greater than the number clustered of the other. We show here that in designing immune complexes that bind with the greatest disparity in number of ligand bound between two receptor kinds of non-negligible affinity, the most important parameters to consider are the avidity of the immune complex and its rates of cross-linking and breaking cross-links between receptors. We further show that most of these complexes fall under two structural motifs.
\end{abstract}
\begin{document}

\flushbottom
\maketitle

\thispagestyle{empty}

\input{Introduction}

%\input{Methods}

\input{Results}

\input{Discussion}

\section*{Acknowledgements}

The authors would like to thank Anja Lux and Falk Nimmerjahn for critical input. This work was supported by NIH DP5-OD019815 to A.S.M. \textbf{Competing financial interests:} The authors declare no competing financial interests.

\section*{Author contributions statement}

A.S.M. conceived the experiment(s),  A.S.M. and R.A.R. conducted the experiment(s), A.S.M. and R.A.R. analyzed the results.  All authors reviewed the manuscript. 

%a -> Lux 2013
%b -> Stone 2001
%c -> Perelson 1981
%d -> Bruhns
%e -> Paper presenting Metropolis-Hastings algorithm for the first time
%%f -> https://www.biosearchtech.com/tnpbsa-bovine-serum-albumin
%g -> \textit{Akaike Information Criterion Statistics}
%h -> mhsample documentation from MATLAB?

\end{document}